Active Object Search with a Mobile Device\\for People with Visual Impairments

### 2018-12-28 review_edition/reviewed.tex
some tidy up of sec 5 and 6

\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
% This section discusses the experiments and their results.

@@

\begin{table}
  \centering
  \caption{A table containing the results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
  \begin{tabular}{cccc}
    \toprule
    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
    \bottomrule                    
  \end{tabular}                    
\end{table}

\begin{table}                      
  \centering                       
  \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
  \begin{tabular}{ccc}
    \toprule
    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
			      & Simulation & 99.7 \\ \midrule
    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
			        & Simulation & 5.4 \\ \midrule
    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{../figures/cdf_tar_limit.png}
  \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{../figures/tar_objects.png}
  \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_steps.png}
  \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_time.png}
  \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
\end{figure}

In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable. However, these results may greatly change when we test the system with participants with vision impairments.

>>>>

\noindent To evaluate our system, we designed a set of experiments that determined how effective the MDP and its policies are at guiding the user in an object search task with the smartphone's camera.
% This section discusses the experiments and their results.

@@

\begin{table}
  \centering
  \caption{Results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
  \begin{tabular}{cccc}
    \toprule
    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
    \bottomrule                    
  \end{tabular}                    
\end{table}

\begin{table}[b]                      
  \centering                       
  \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
  \begin{tabular}{ccc}
    \toprule
    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
			      & Simulation & 99.7 \\ \midrule
    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
			        & Simulation & 5.4 \\ \midrule
    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[b]
  \centering
  \includegraphics[height=5.9cm]{../figures/cdf_tar_limit.png}
  \caption{TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../figures/tar_objects.png}
  \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
\end{figure}

@@

\begin{figure}[b]
  \centering
  \includegraphics[height=5.9cm]{../figures/cdf_total_steps.png}
  \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../figures/cdf_total_time.png}
  \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
\end{figure}

In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable, although there might be significant variations in case of participants with vision impairments.
